---
title: "APA&Co project | Results shown in the manuscript"
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    df_print: paged
    code_folding: hide
toc-title: "Table of content"

---
```{css, echo=FALSE}
.title {
  font-weight: bold;
}


h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 21px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
p {
  font-size: 20px;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
library(hopkins)
library(performance)
ggplot2::theme_set(ggplot2::theme_bw())
tar_load(DB_EMAPS_0_12_M0_scaled)
tar_load(DB_EMAPS_0_12_M12_scaled)
```

# Descriptive analysis of the participants
## Overview
```{r inclusion_analysis}
targets::tar_read(analysis_INCLUSION)
```

## Sex (1 = men; 2 = women)
```{r sex_analysis}
targets::tar_read(analysis_sex)
```

## Age
```{r age_analysis}
targets::tar_read(analysis_age)
```

## Height
```{r height_analysis}
targets::tar_read(analysis_height)
```

## Weight
```{r weight_analysis}
targets::tar_read(analysis_weight)
```

## Body mass index
```{r bmi_analysis}
targets::tar_read(analysis_bmi)
```

## Angioplasty (0 = no angioplasty; 1 = with angioplasty)
```{r angioplasty_analysis}
targets::tar_read(analysis_angioplasty)[, c(1:2)]
```

## Bypass (0 = no bypass; 1 = with bypass)
```{r bypass_analysis}
targets::tar_read(analysis_bypass)[, c(1:2)]
```

# Change in 6MWT distance between 0 and 12 months
## Descriptive statistics
```{r 6MWT_desc_stats}
targets::tar_read(DB_6MWT_0_12) |> 
  dplyr::select(-n_visits) |>   
  dplyr::group_by(MONTH) |> 
  skimr::skim()
```

## T-test
```{r 6MWT_ttest}
targets::tar_read(t_test_results_6MWT)
```

## Pearson correlation
```{r 6MWT_corr}
# Rearrange data
data_6MWT <- 
  targets::tar_read(DB_6MWT_0_12) |> 
  tidyr::pivot_wider(names_from = MONTH, values_from = DIST_M)

# Compute Pearson correlation
cor.test(data_6MWT$`0`, data_6MWT$`12`)
```

## Effect size (dav)
```{r 6MWT_dav}
mean_diff <- mean(data_6MWT$`12` - data_6MWT$`0`)
sd1 <- sd(data_6MWT$`0`)
sd2 <- sd(data_6MWT$`12`)
dav <- mean_diff / sqrt(((sd1^2 + sd2^2) / 2))
round(dav, 2)
```

## Estimate of the median of the individual changes
```{r 6MWT_median_change}
tar_read(change_6MWT)$hd_pbci_diff |> 
  dplyr::filter(q == 0.5)  |> 
  dplyr::mutate(dplyr::across(estimate:ci_u, ~round(.x, digits = 2)))
```

## Shift and difference asymmetry functions
```{r 6MWT_shift_function, fig.width=20, fig.height=16, fig.cap='Change in 6-min walking test (6MWT) distance between 0 and 12 months (N = 75). On panel A, the errors bars over the points are the standard deviations around the means, while on panel D it is the percentile bootstrap 95% confidence interval around the median estimate. On panels E and F, the error bars are percentile bootstrap 95% confidence intervals non corrected for multiple comparisons. On panels B, C and D, the horizontal and/or vertical segments are the estimates of the deciles (panels B and C) or the quantiles (panel D, step of 0.05) of the distributions; the thickest segments are the median estimates. On panel B, the diagonal black line depicts the identity line. If any, significant results (based on adjusted p-values) in the shift (panel E) and difference asymmetry (panel F) functions are highlighted using thick red circles. A small pseudo-random movement has been added horizontally and vertically to the raw data displayed on panel B to minimize the presence of points fully overlapped. The estimates of the deciles of the marginal distributions (panels B, C and D), the quantiles of the individual differences (panel D), the decile differences (panel E) and the quantile sums (panel F) have been computed using the Harrell-Davis estimator.'}
targets::tar_read(change_6MWT)$p
```

# Change in IPAQ MET-min/week between 6 and 12 months
## Descriptive statistics
```{r IPAQ_desc_stats}
targets::tar_read(DB_IPAQ_6_12) |>
  dplyr::select(-n_visits) |>  
  dplyr::group_by(MONTH) |> 
  skimr::skim()
```

## Estimate of the median of the individual changes
```{r IPAQ_median_change}
tar_read(change_IPAQ_6_12)$hd_pbci_diff |> 
  dplyr::filter(q == 0.5) |> 
  dplyr::mutate(dplyr::across(estimate:ci_u, ~round(.x, digits = 2)))
```

## Shift and difference asymmetry functions
```{r IPAQ_shift_function, fig.width=22, fig.height=16, fig.cap='Change in IPAQ-SF MET-min/week between 6 and 12 months (N = 77). On panel A, the errors bars over the points are the standard deviations around the means, while on panel D it is the percentile bootstrap 95% confidence interval around the median estimate. On panels E and F, the error bars are percentile bootstrap 95% confidence intervals non corrected for multiple comparisons. On panels B, C and D, the horizontal and/or vertical segments are the estimates of the deciles (panels B and C) or the quantiles (panel D, step of 0.05) of the distributions; the thickest segments are the median estimates. On panel B, the diagonal black line depicts the identity line. If any, significant results (based on adjusted p-values) in the shift (panel E) and difference asymmetry (panel F) functions are highlighted using thick red circles. A small pseudo-random movement has been added horizontally and vertically to the raw data displayed on panel B to minimize the presence of points fully overlapped. The estimates of the deciles of the marginal distributions (panels B, C and D), the quantiles of the individual differences (panel D), the decile differences (panel E) and the quantile sums (panel F) have been computed using the Harrell-Davis estimator.'}
targets::tar_read(change_IPAQ_6_12)$p
```

# Change in EMAPS scores between 0 and 12 months
## Descriptive statistics
```{r emaps_desc_stats}
targets::tar_read(DB_EMAPS_0_12) |> 
  dplyr::select(-n_visits) |>  
  dplyr::group_by(MONTH) |> 
  skimr::skim()
```

## Estimates of the medians of the individual changes
```{r emaps_median_change, results = "asis"}
targets::tar_load(change_EMAPS)
res <-
  purrr::map(change_EMAPS, function(x) {
  
  knitr::knit_child(text = c(
                    
                    "\n",
                    "### `r x$variable`",
                    "\n",
                    "```{r, echo = FALSE}",
                    "x$hd_pbci_diff |>  
                     dplyr::filter(q == 0.5) |> 
                     dplyr::mutate(dplyr::across(estimate:ci_u, ~round(.x, digits = 2)))",
                    "```"
  ),
  envir = environment(),
  quiet  = TRUE
  )
})

cat(unlist(res), sep = "\n")
```

# Change in profile of motivation for physical activity
## Assess cluster tendency
### Graphically inspect data using principal component analysis
```{r inspect_data_with_pca}
targets::tar_read(p_pca)
```

### Confirm cluser tendency using graphical method
```{r assess_cluster_tendency_viz, fig.cap="Red: high similarity (ie: low dissimilarity) | Blue: low similarity"}
targets::tar_read(cluster_tendency)
```

### Confirm cluser tendency using the Hopkins statistic
#### Hopkins statistic for the dataset at month 0
```{r assess_cluster_tendency_stat_m0}
set.seed(123)
hopkins(DB_EMAPS_0_12_M0_scaled)
```

Comment: Data seem clustered (Hopkins statistic >0.7).

#### Hopkins statistic for the dataset at month 12
```{r assess_cluster_tendency_stat_m12}
set.seed(123)
hopkins(DB_EMAPS_0_12_M12_scaled)
```

Comment: Data seem clustered (Hopkins statistic >0.7).

## Check outliers relating to a multivariate setting
### Month 0
```{r check_outliers_m0}
check_outliers(DB_EMAPS_0_12_M0_scaled, method = "mcd")
```

### Month 12
```{r check_outliers_m12}
check_outliers(DB_EMAPS_0_12_M12_scaled[, c(names(DB_EMAPS_0_12_M12_scaled)[1:5])], method = "mcd") 
# removed AMOTIVATION variable that caused an error due to an IQR of 0.
```

## Determine the optimal number of clusters for K-Medoid approach using the silhouette method
```{r, get_optimal_clusters_number_emaps}
targets::tar_read(optim_n_clusters)
```

Comment : The optimal number of clusters related to the K-Medoid approach is 2 at both 0 and 12 months post-program (according to the silhouette method).

## Visualize the final clusters using K-Medoid approach
```{r get_final_clusters_emaps}
targets::tar_read(final_clusters_emaps_viz)
```

## Visualize the EMAPS descriptive statistics related the motivation profiles (clusters)
```{r viz_clusters, fig.width=15}
targets::tar_read(p_emaps_clust)
```

```{r show_desc_stats_by_cluster_emaps_tab, rows.print=14}
targets::tar_read(table_stats_clusters_emaps)
```

## Compare motivation profiles
### Comparison at Month 0
#### Global analysis
```{r, nonpartest_global_month0}
targets::tar_read(nonpartest_global_month0)
```

#### Localisation of the difference(s)
```{r, nonpartest_local_month0}
ssnonpartest(IDENTIFIED | INTROJECTED | EXTERNAL | AMOTIVATION ~ cluster, data = tar_read(DB_EMAPS_0_12_clust) |> filter(MONTH == "0"), test = c(1, 0, 0, 0), alpha = 0.05, factors.and.variables = TRUE)
```

### Comparison at Month 12
#### Global analysis
```{r, nonpartest_global_month12}
targets::tar_read(nonpartest_global_month12)
```

#### Localisation of the difference(s)
```{r, nonpartest_local_month12}
ssnonpartest(IDENTIFIED | INTROJECTED | EXTERNAL | AMOTIVATION ~ cluster, data = tar_read(DB_EMAPS_0_12_clust) |> filter(MONTH == "12"), test = c(1, 0, 0, 0), alpha = 0.05, factors.and.variables = TRUE)
```

## Characterize the change in motivation profile
### Visualize the change in motivation profile
```{r, change_emaps_profile_alluvial}
targets::tar_read(change_emaps_profile_alluvial)
```

### Visualize the EMAPS score deltas depending on the cluster transition
```{r, p_DB_EMAPS_0_12_diffs}
targets::tar_read(p_DB_EMAPS_0_12_diffs)
```

### Compare the EMAPS scores between month 0 and month 12 for participants who stayed in the 'Very High AU-High C' cluster
```{r, compa_intra_clust_VHAUHC}
targets::tar_read(compa_intra_clust_VHAUHC)
```

### Compare the EMAPS scores between month 0 and month 12 for participants who stayed in the 'High AU-Mod C' cluster
```{r, compa_intra_clust_HAUMODC}
targets::tar_read(compa_intra_clust_HAUMODC)
```

### Compare the EMAPS scores between month 0 and month 12 for participants who transited from the 'Very High AU-Mod C' to the 'High AU-Mod C' cluster
```{r, compa_intra_clust_VHAUHC_to_HAUMODC}
targets::tar_read(compa_intra_clust_VHAUHC_to_HAUMODC)
```

### Compare the EMAPS scores between month 0 and month 12 for participants who transited from the 'High AU-Mod C' to the 'Very High AU-High C' cluster
```{r, compa_intra_clust_HAUMODCto_VHAUHC}
targets::tar_read(compa_intra_clust_HAUMODCto_VHAUHC)
```

# Barriers to physical activity at 12 months
```{r, fig.width=12, fig.height=8, fig.cap='Barriers to physical activity (N = 77). Answers have been translated from French to English for the reader’s understanding of the figure. The most frequently evocated barriers have been highlighted with darker colours.'}
targets::tar_read(p_BARRIERS)
```


