---
title: "APA&Co project | Results shown in the manuscript"
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    df_print: paged
    code_folding: hide
toc-title: "Table of content"

---
```{css, echo=FALSE}
.title {
  font-weight: bold;
}


h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 21px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
ggplot2::theme_set(ggplot2::theme_bw())
```

# Descriptive analysis of the participants
## Overview
```{r}
targets::tar_read(analysis_INCLUSION)
```

## Sex (1 = men; 2 = women)
```{r}
targets::tar_read(analysis_sex)
```

## Age
```{r}
targets::tar_read(analysis_age)
```

## Height
```{r}
targets::tar_read(analysis_height)
```

## Weight
```{r}
targets::tar_read(analysis_weight)
```

## Body mass index
```{r}
targets::tar_read(analysis_bmi)
```

## Angioplasty (0 = no angioplasty; 1 = with angioplasty)
```{r}
targets::tar_read(analysis_angioplasty)[, c(1:2)]
```

## Bypass (0 = no bypass; 1 = with bypass)
```{r}
targets::tar_read(analysis_bypass)[, c(1:2)]
```

# Change in 6MWT distance between 0 and 12 months
## Descriptive statistics
```{r}
targets::tar_read(DB_6MWT_0_12) |> 
  dplyr::group_by(MONTH) |> 
  skimr::skim()
```

## T-test
```{r}
targets::tar_read(t_test_results_6MWT)
```

## Pearson correlation
```{r}
# Rearrange data
data_6MWT <- 
  targets::tar_read(DB_6MWT_0_12) |> 
  tidyr::pivot_wider(names_from = MONTH, values_from = DIST_M)

# Compute Pearson correlation
cor.test(data_6MWT$`0`, data_6MWT$`12`)
```

## Effect size (dav)
```{r}
mean_diff <- mean(data_6MWT$`12` - data_6MWT$`0`)
sd1 <- sd(data_6MWT$`0`)
sd2 <- sd(data_6MWT$`12`)
dav <- mean_diff / sqrt(((sd1^2 + sd2^2) / 2))
dav
```

## Shift and difference asymmetry functions
```{r, fig.width=20, fig.height=16, fig.cap='Change in 6-min walking test (6MWT) distance between 0 and 12 months (N = 75). On panels A and D, the error bars over the points are the standard deviations around the means. On panels E and F, the error bars are the percentile bootstrap 95% confidence intervals non corrected for multiple comparisons. On panel B, the black line depicts the identity line. If any, significant results (based on adjusted p-values) in the shift (panel E) and difference asymmetry (panel F) functions are highlighted using thick red circles. A small pseudo-random movement has been added horizontally and vertically to the raw data displayed on panel B to minimize the presence of points fully overlapped. The decile differences (panels C and E) and the quantile sums (panel F) have been computed using the Harrel-Davis estimator.'}
targets::tar_read(change_6MWT)$p
```

# Change in IPAQ MET-min/week between 6 and 12 months
## Descriptive statistics
```{r}
targets::tar_read(DB_IPAQ_6_12) |> 
  dplyr::group_by(MONTH) |> 
  skimr::skim()
```

## Shift and difference asymmetry functions
```{r, fig.width=22, fig.height=16, fig.cap='Change in IPAQ-SF MET-min/week between 6 and 12 months (N = 77). On panels A and D, the error bars over the points are the standard deviations around the means. On panels E and F, the error bars are the percentile bootstrap 95% confidence intervals non corrected for multiple comparisons. On panel B, the black line depicts the identity line. If any, significant results (based on adjusted p-values) in the shift (panel E) and difference asymmetry (panel F) functions are highlighted using thick red circles. A small pseudo-random movement has been added horizontally and vertically to the raw data displayed on panel B to minimize the presence of points fully overlapped. The decile differences (panels C and E) and the quantile sums (panel F) have been computed using the Harrel-Davis estimator.'}
targets::tar_read(change_IPAQ)$p
```

# Barriers to physical activity at 12 months
```{r, fig.width=12, fig.height=8, fig.cap='Barriers to physical activity (N = 77). Answers have been translated from French to English for the reader’s understanding of the figure. The most frequently evocated barriers have been highlighted with darker colours.'}
targets::tar_read(p_BARRIERS)
```


