---
output: github_document
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = FALSE,
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-",
  out.width = "100%"
)
```

# APACo
## Get an overview of the package
This package was build to perform, share, and reproduce the analytical pipeline implemented to get the results of the 'APA&Co' project ([ClinicalTrials.gov ID: NCT04732923](https://clinicaltrials.gov/study/NCT04732923?term=APA%26Co&rank=4)). Briefly, the 'APA&Co' project was conducted to observe the maintainance of physical condition, physical activity, and motivation for physical activity in coronary artery disease patients at 1 year after following a cardiac rehabilitation program. This research project was managed by the hospital center of Cholet (France). This package is not intented to provide functions that could be reused in other projects. Some of the functions actually could be used for this purpose, but most of them were designed only to work with the data of the project.

The package includes the raw data as well as all the materials required to reproduce the analyses of the project.

## Reproduce the analytical pipeline
The analytical pipeline implemented to the get the results of the project is based on packages that have been designed to make all analyses reproducible: the {renv} package, and the {targets} package. {renv} will allow you to restore all the exact package dependencies that have been used to perform analyses and to get the final materials of the project. {target} will provide you the structure to automatically drive the analyses. Please follow the steps below if you want to reproduce the analyses of the project.

* Step 1: Intall R and RStudio on your PC.
* Step 2: Download the zip file of the {APACo} package and unzip it on your PC.
* Step 3 : Open the project in RStudio by double-clicking on the .Rproj file of the unzipped folder.
* Step 4: Restore the package dependencies of the project with {renv} using the following command line in the Console:
```{r, eval = FALSE}
renv::restore()
```

* Step 5: Run the analytical pipeline with {targets} using the following command line in the Console:
```{r, eval = FALSE}
targets::tar_make()
```

This last step will produce all the objects created for the required analyses. It also will generate .html files corresponding to the materials considered for scientific publication. Some materials may take time to be built, so please be patient.

Once the analytical pipeline ended, you will can access any created object using `targets::tar_read(OBJECT_NAME)` to read it in the Console or the viewer pane depending on the class of the object, or using `targets::tar_load(OBJECT_NAME)` to load the object in the global environment. You can load all the created objects using `targets::tar_load_everything()`. All the figures and .html reports will appear in a new 'out/' folder placed at the root of the project during the run of the analytical pipeline.

## Verify the code
If you want to look at the code implemented in the functions of the {APACo} package used for the analyses, please take a look at the dedicated [Github repository](https://github.com/pydemull/APACo). The files placed in the 'R/' folder are what you want.

