---
title: "SM4. Figures relating to the change in EMAPS scores between 0 and 12 months (N = 76)"
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    df_print: paged
toc-title: "Table of content"
---
```{css, echo=FALSE}
.title {
  font-weight: bold;
}


h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 21px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message=FALSE)
ggplot2::theme_set(theme_bw())
targets::tar_load(change_EMAPS)
```

```{r, results = "asis"}
res <-
  purrr::map(change_EMAPS, function(x) {
  
  knitr::knit_child(text = c(
                    
                    "\n",
                    "# `r x$variable`",
                    "\n",
                    "```{r, echo = FALSE, fig.width = 20, fig.height = 20, dpi = 250, fig.cap = 'On panels A and C, the error bars over the points are the standard deviations around the means. On panels D and F, the error bars are 95% confidence intervals non corrected for multiple comparisons. On panel E, the black line depicts the identity line. If any, significant results (based on adjusted p-values) in the shift (panel D) and difference asymmetry (panel F) functions are highlighted using thick red circles. A small pseudo-random movement has been added horizontally and vertically to the raw data displayed on panel E to minimize the presence of points fully overlapped.'}",
                    "print(x$p)",
                    "```"
  ),
  envir = environment(),
  quiet  = TRUE
  )
})

cat(unlist(res), sep = "\n")
```

