---
title: "SM4. Data relating to the shift and difference asymmetry functions to describe the change in 6MWT, IPAQ-SF and EMAPS scores during the APA & Co study"
output: 
  html_document:
    theme: cosmo
    toc: yes
    toc_depth: 2
    toc_float: yes
    number_sections: yes
    df_print: paged
toc-title: "Table of content"
params:
  change_6MWT: NA
  change_IPAQ: NA
  change_emaps: NA
---
```{css, echo=FALSE}
.title {
  font-weight: bold;
}


h1 {
  font-size: 25px;
  font-weight: bold;
}
h2 {
  font-size: 23px;
  font-weight: bold;
}
h3 {
  font-size: 21px;
}
p.caption {
  color: #777;
  margin-top: 10px;
}
p code {
  white-space: inherit;
}
pre {
  word-break: normal;
  word-wrap: normal;
}
pre code {
  white-space: inherit;
}
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning=FALSE, message = FALSE)
```

# Six-minute walking test
## Shift function
```{r}
change_6MWT$sf
```

## Difference asymetry function
```{r}
change_6MWT$daf
```


# IPAQ-SF MET-min / week
## Shift function
```{r}
change_IPAQ$sf
```

## Difference asymetry function
```{r}
change_IPAQ$daf
```


# EMAPS | Intrinsic motivation
## Shift function
```{r}
change_emaps[[1]][[2]]$sf
```

## Difference asymetry function
```{r}
change_emaps[[1]][[2]]$daf
```


# EMAPS | Integrated regulation
## Shift function
```{r}
change_emaps[[2]][[2]]$sf
```

## Difference asymetry function
```{r}
change_emaps[[2]][[2]]$daf
```


# EMAPS | Identified regulation
## Shift function
```{r}
change_emaps[[3]][[2]]$sf
```

## Difference asymetry function
```{r}
change_emaps[[3]][[2]]$daf
```


# EMAPS | Introjected regulation
## Shift function
```{r}
change_emaps[[4]][[2]]$sf
```

## Difference asymetry function
```{r}
change_emaps[[4]][[2]]$daf
```


# EMAPS | External regulation
## Shift function
```{r}
change_emaps[[5]][[2]]$sf
```


## Difference asymetry function
```{r}
change_emaps[[5]][[2]]$daf
```


# EMAPS | Amotivation
## Shift function
```{r}
change_emaps[[6]][[2]]$sf
```

## Difference asymetry function
```{r}
change_emaps[[6]][[2]]$daf
```



